Global Distribution of Unintended Pregnancies and Contraceptive Usage

### 2024-02-23 products/manuscript/Manuscript.qmd
Attempted Knit
I tried to knit the manuscript document, but I am getting an error that it cannot find an object that it was created in the eda.qmd file.

```{r, echo=FALSE, message=FALSE}
xcode-select --install
# load a few R packages
install.packages("dplyr")
install.packages("naniar")
library(here)
library(readr)
library(knitr)
library(dplyr)
library(naniar)
library(ggplot2)
```
## Project Part 1  
# Data Source 
The data source for this project is the Guttmacher Institute, which is a well-known research organization focusing on improving sexual and reproductive health around the world. The data used here is from their Adding It Up project. The goals of this project include estimating the need for, impact of, and costs associated with providing sexual and reproductive health services. Low and middle income countries are the target audience for this research, specifically women of reproductive age (15-49). Some of the variables included in this dataset are modern contraceptive use, unintended pregnancies, unplanned births, and abortions averted. Observations are drawn from nationally representative surveys, including Demographic and Health Surveys, UNICCEF Multiple Indicator Cluster Surveys, US Centers for Disease Control Reproductive Health Surveys, Performance Monitoring for Action Surveys, and others. The UN Population Division is the source of population projections for women in this age group, and estimates of unintended pregnancies are from the Guttmacher Institute, WHO, and other authors, which have been adjusted to 2019.

@@

# Project Part 2
# Exploring and processing the data 
The first priority when cleaning the data was analyzing missing values. We found that the `pct_upreg` variable containing the percentage of unintended pregnancies is unreliable due to missing data that could not be explained. We decided to use the variables with percentage of unintended pregnancies related to each birth control method as our outcome variables because they are complete and were found directly based on the AIU protocol information. We printed the summary table here becacuse it was useful in determining missingness and creating a new factor variable for the usage of each birth control method at the factor level later in the processing sequence. 
```{r}
# show summary table to numeric variables with misssing values
print(summary_df)
```
We explored the distribution of the countries by five categorical variables: `region`, `larcster_usage`, `sarc_usage`, `trad_usage`, and `none_usage`. We found that most countries are located in Africa followed by Asia and Latin America/the Caribbean. Only 20 countries have high usage of long acting reversible and sterilization methods compared to 33 countries with high usage of short acting reversible and traditional methods. It is interesting that the distributions for short acting reversible method, traditional method, and no method usages are the same. 
```{r}
print(summary_table)
```

>>>>

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(readr)
library(knitr)
library(dplyr)
library(naniar)
library(ggplot2)
```
## Project Part 1  
# Data Source 
The data source for this project is the Guttmacher Institute, which is a well-known research organization focusing on improving sexual and reproductive health around the world. The data used here is from their Adding It Up project. The goals of this project include estimating the need for, impact of, and costs associated with providing sexual and reproductive health services. Low and middle income countries are the target audience for this research, specifically women of reproductive age (15-49). Some of the variables included in this dataset are modern contraceptive use, unintended pregnancies, unplanned births, and abortions averted. Observations are drawn from nationally representative surveys, including Demographic and Health Surveys, UNICCEF Multiple Indicator Cluster Surveys, US Centers for Disease Control Reproductive Health Surveys, Performance Monitoring for Action Surveys, and others. The UN Population Division is the source of population projections for women in this age group, and estimates of unintended pregnancies are from the Guttmacher Institute, WHO, and other authors, which have been adjusted to 2019.

@@

# Project Part 2
# Exploring and processing the data 
The first priority when cleaning the data was analyzing missing values. We found that the `pct_upreg` variable containing the percentage of unintended pregnancies is unreliable due to missing data that could not be explained. We decided to use the variables with percentage of unintended pregnancies related to each birth control method as our outcome variables because they are complete and were found directly based on the AIU protocol information. We printed the summary table here because it was useful in determining missingness and creating a new factor variable for the usage of each birth control method at the factor level later in the processing sequence. 
```{r}
# show summary table to numeric variables with missing values
print(summary_df)
```
We explored the distribution of the countries by five categorical variables: `region`, `larcster_usage`, `sarc_usage`, `trad_usage`, and `none_usage`. We found that most countries are located in Africa followed by Asia and Latin America/the Caribbean. Only 20 countries have high usage of long acting reversible and sterilization methods compared to 33 countries with high usage of short acting reversible and traditional methods. It is interesting that the distributions for short acting reversible method, traditional method, and no method usages are the same. 
```{r}
print(summary_table)
```
